Items

### 2024-04-12 index.Rmd
deleting large files

- You can either read the paper [in your browser](proposal.html) or download it as [pdf](proposal.pdf). 
- You can also find the detailed code and summaries of the [analyses](analyses.html) reported in the paper

This website is produced directly from the project's [github repository](https://github.com/tdienlin/who_needs_privacy_rr). You can download the material and the data, file an issue, or submit a pull request.

>>>>

- You can either read the paper [in your browser](manuscript.html) or download it as [pdf](manuscript.pdf). 
- You can also read the [Stage 1 submission](proposal.html).
- The data are shared on [AUSSDA](https://data.aussda.at/citation?persistentId=doi:10.11587/IC66GC) and can be used for scientific purposes.

This website is produced directly from the project's [github repository](https://github.com/tdienlin/who_needs_privacy_rr). You can download the material, file an issue, or submit a pull request.

### 2024-04-12 items.rmd
deleting large files

---
title: "Items"
output:
  html_document:
    toc: TRUE
    toc_float:
      collapsed: FALSE
      toc_depth: 3
# output: pdf_document
bibliography: 
  - "bibliography/references.bib"
---

@@

(-3) Strongly Disagree, (-2) Disagree, (-1) Slightly Disagree, (0) Neutral, (1) Slightly Agree (2) Agree, (3) Strongly Agree

@@

 1. < \$1.000
 2. \$1.000 - \$4.000
 3. > \$4.000

>>>>

---
title: "Items"
subtitle: "Data-set: Need for Privacy and Personality"
author: "Tobias Dienlin & Miriam Metzger"
date: "2024-04-05"
# output:
#   html_document:
#     toc: TRUE
#     toc_float:
#       collapsed: FALSE
#       toc_depth: 3
output:
  pdf_document:
    toc: TRUE
    toc_depth: 1
bibliography: 
  - "bibliography/references.bib"
---

# Suggested citation

Dienlin, Tobias; Metzger, Miriam, 2024, "Need for Privacy and Personality", https://doi.org/10.11587/IC66GC, AUSSDA.

This document is licenced under a [Creative Commons Attribution 4.0 International Licence](https://creativecommons.org/licenses/by/4.0/).

```{r, out.width = "200px", fig.align='center', echo=F}
knitr::include_graphics("../Data/license.png")
```

\newpage

# Overview

 <!-- - For a pdf of all items, click here. -->
 <!-- - For the actual questionnaire, click here. -->

@@

(-3) Strongly Disagree, (-2) Disagree, (-1) Somewhat Disagree, (0) Neutral, (1) Somewhat Agree (2) Agree, (3) Strongly Agree

@@

 1. < \$1.000
 2. \$1.000 - \$4.000
 3. \> \$4.000
